% about section

\section{experience}

\begin{entrylist}
  \entry
    {2012-Present}
    {Senior Performance Engineer}
    {Los Gatos, CA}
    {
      \textbf{Netflix}
      \begin{itemize}
        \item Optimize service reliability and performance, and help scale Netflix's high-traffic, large-scale distributed systems.
        \item Thorough performance analysis and tuning across all services and layers.
        \item Find optimizations both within application stacks and across the infrastructure.
        \item Develop effective observability tooling and and assist with production triage and root cause analysis on performance or availability issues.  
      \end{itemize}
      \begin{itemize}
        \item Created Vector, Netflix's open source on-host, high-resolution performance monitoring framework.
        \item Drove a company-wide program to improve service availability by implementing and applying a collection of best practices related to the development, deployment, and operation of cloud services.
        \item Developed Mogul, a bottleneck analysis tool that inspects internal and downstream dependency demand for services.
        \item Developed Slalom, a high-level demand analysis tool that helps visualize demand flow on large scale systems.
        \item Created a performance trend report to help identify long-term performance regression.
        \item Implemented and extended the capabilities of the in-house performance testing framework.
        \item Developed and supported the performance analysis tool with fully automated analysis capabilities.
        \item Drove performance test adoption company-wide and integration on continuous integration environments.
      \end{itemize}
    }
  \entry
    {2011-2012}
    {Performance Engineer}
    {Bellevue, WA}
    {
      \textbf{Expedia}
      \begin{itemize}
        \item Responsible for ensuring the performance, stability and scalability of large scale platforms that support the Hotels, Flights, Cars and Ads LOBs.
        \item Led the performance engineering effort during the first two full LOB migrations to the new Java platform based on Tomcat, Hotels and Flights, and also the Ads engine, DoubleClick, to Linux.
        \item Improved early issue discovery and quality cost by introducing performance tests to the Continuous Delivery pipeline using HP Performance Center, Jenkins and in-house developed tools.
        \item Promoted awareness about performance related issues by introducing an executive dashboard and alerting system for Trunk performance test executions.
        \item Deployed and maintained the client-side performance evaluation tool based on the open-source project WebPagetest.
        \item Introduced JVM MBean and Linux monitoring to performance tests through HP SiteScope and Java code profiling with YourKit.
        \item Introduced the concept of Java heap trend analysis by linear regression.
        \item Contributed to the team’s process standardization by developing test plan and report standards, and introduced an environment reservation system.
        \item Supported performance test execution by non-performance engineering resources, including functional testers and developers, and coached offshore resources in China.
      \end{itemize}
    }
  \entry
    {2007-2011}
    {Performance Engineer}
    {Porto Alegre, Brazil}
    {
      \textbf{Dell}
      \begin{itemize}
        \item Led a team of 4 performance engineers responsible for one of the most critical Dell business streams, working mostly on large and global projects, with 50+ critical applications in scope.
        \item Responsible for the team’s development, capacity planning, project allocation and structure definition.
        \item Led the performance research group in conjunction with a local university, focusing on performance of virtualized environments, performance modeling and performance engineering tools.
        \item Coordinated the alignment between cross functional teams, including development, functional test, architecture and infrastructure, spread across multiple locations  in the USA, India, UK, France, Russia, Malaysia, Singapore and Japan.
        \item Led the performance test efforts for the largest IT project in 2009 and 2010 that aimed to replace Dell’s worldwide order management system and quoting engine.
        \item Contributed significantly to the team’s process standardization initiative by creating standards for plans and reports and defining the standard life cycle for performance engineering projects.
        \item Specialized on several technologies, including Oracle EBS, Oracle WebLogic, Citrix, Microsoft IIS, Web Services, IBM MQ, .NET Framework, Oracle Database and Microsoft SQL Server.
      \end{itemize}
    }
  \entry
    {2006-2007}
    {Software Test Analyst}
    {Porto Alegre, Brazil}
    {
      \textbf{Dell}
      \begin{itemize}
        \item Part of Dell’s first major project in the Brazil development center, with benefits surpassing U\$3.842.294 (estimated for one fiscal year).
        \item Led all functional test efforts for 3 out of 10 applications in scope and had 0\% defect leakage to production, automating all test cases using HP QTP.
        \item Led a team of 4 performance engineers responsible for one of the most critical Dell business streams, working mostly on large and global projects, with 50+ critical applications in scope.
        \item Responsible for the team’s development, capacity planning, project allocation and structure definition.
        \item Led the performance research group in conjunction with a local university, focusing on performance of virtualized environments, performance modeling and performance engineering tools.
        \item Coordinated the alignment between cross functional teams, including development, functional test, architecture and infrastructure, spread across multiple locations  in the USA, India, UK, France, Russia, Malaysia, Singapore and Japan.
        \item Led the performance test efforts for the largest IT project in 2009 and 2010 that aimed to replace Dell’s worldwide order management system and quoting engine.
        \item Contributed significantly to the team’s process standardization initiative by creating standards for plans and reports and defining the standard life cycle for performance engineering projects.
        \item Specialized on several technologies, including Oracle EBS, Oracle WebLogic, Citrix, Microsoft IIS, Web Services, IBM MQ, .NET Framework, Oracle Database and Microsoft SQL Server.
      \end{itemize}
    }
\end{entrylist}
