\section{open source}

\textbf{FlameScope}
\newline
\vspace{\parsep}
{\addfontfeature{Color=lightgray} \href{https://github.com/Netflix/flamescope}{github.com/Netflix/flamescope}}
\newline
FlameScope is a visualization tool for exploring different time ranges as Flame Graphs, allowing quick analysis of performance issues such as perturbations, variance, single-threaded execution, and more.
\newline
FlameScope begins by displaying the input data as an interactive subsecond-offset heat map. This shows patterns in the data. You can then select a time range to highlight on different patterns, and a flame graph will be generated just for that time range.
\newline
\vspace{\parsep}

\textbf{Vector}
\newline
\vspace{\parsep}
{\addfontfeature{Color=lightgray} \href{https://github.com/Netflix/vector}{github.com/Netflix/vector}}
\newline
An open source on-host performance monitoring framework which exposes hand picked high resolution system and application metrics to every engineer’s browser.
\newline
\vspace{\parsep}

\textbf{d3-flame-graph}
\newline
\vspace{\parsep}
{\addfontfeature{Color=lightgray} \href{https://github.com/spiermar/d3-flame-graph}{github.com/spiermar/d3-flame-graph}}
\newline
A d3.js plugin that produces flame graphs from hierarchical data.
\newline
\vspace{\parsep}

\textbf{d3-heatmap2}
\newline
\vspace{\parsep}
{\addfontfeature{Color=lightgray} \href{https://github.com/spiermar/d3-heatmap2}{github.com/spiermar/d3-heatmap2}}
\newline
A d3.js plugin that produces heatmaps.
\newline
\vspace{\parsep}

\textbf{burn}
\newline
\vspace{\parsep}
{\addfontfeature{Color=lightgray} \href{https://github.com/spiermar/burn}{github.com/spiermar/burn}}
\newline
A CLI tool to convert performance profiles (Linux perf, pprof, etc) to hierarchical data structure that can be visualized as flame graphs, with the help of the d3-flame-graph plugin. burn can also generate a self contained html flame graphs from the same data.
\newline
\vspace{\parsep}
